State of the Practice for Lattice Boltzmann Method Software

### 2022-01-09 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
added publications to Tables 1 and 2

\begin{table}
\begin{center}
	\begin{tabular}{ p{3cm}p{2cm}p{2cm}p{7cm} }
		\toprule
		Name & Released & Updated & Relevant Publication\\
		\midrule
		\href{https://www.ccp5.ac.uk/sites/www.ccp5.ac.uk/files/dl_meso/data/dl_meso_2.7.zip}{DL\_MESO (LBE)} & unclear & 2020 Mar&\\
		\href{https://github.com/espressomd/espresso}{ESPResSo} & 2010 Nov & 2020 Jun&\\
		\href{https://github.com/espressopp/espressopp}{ESPResSo++} & 2011 Feb & 2020 Apr&\\
		\href{https://github.com/mabau/lbmpy}{lbmpy}& unclear  & 2020 Jun & \\
		\href{https://github.com/Olllom/lettuce}{lettuce} & 2019 May & 2020 Jul&\\
		\href{https://github.com/ludwig-cf/ludwig}{Ludwig} & 2018 Aug & 2020 Jul&\\
		\href{https://github.com/aharwood2/LUMA}{LUMA} & 2016 Nov   & 2020 Feb &\\
		\href{http://hg.savannah.gnu.org/hgweb/mechsys/file/tip/}{MechSys} & 2008 Jun    & 2021 Oct &\\
		\href{https://osdn.net/projects/apes/scm/hg/musubi/}{Musubi} & 2013 Sep & 2019 Aug &\\
		\href{https://www.openlb.net/download/}{OpenLB} & 2007 Jul & 2019 Oct &\\
		\href{https://gitlab.com/unigespc/palabos}{Palabos} & unclear & 2020 Jul &\\
		\href{https://github.com/pylbm/pylbm}{pyLBM} & 2015 Jun&   2020 Jun &\\
		\href{https://github.com/sailfish-team/sailfish}{Sailfish} & 2012 Nov & 2019 Jun &\\
		\href{https://github.com/CFD-GO/TCLB}{TCLB} & 2013 Jun  & 2020 Apr & Adjoint Lattice Boltzmann for topology optimization on multi-GPU architecture \citep{rokicki2016adjoint}\\
		\href{https://i10git.cs.fau.de/walberla/walberla}{waLBerla} & 2008 Aug & 2020 Jul & WALBERLA: A block-structured high-performance framework for multiphysics simulations \citep{bauer2021walberla}\\
		\bottomrule
	\end{tabular}
	\caption{Alive Software Packages} \label{alivepackages}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
	\begin{tabular}{ p{3cm}p{2cm}p{2cm}p{7cm} }
		\toprule
		Name & Released & Updated & Relevant Publication\\
		\midrule
		\href{https://github.com/UCL/hemelb}{HemeLB} & 2007 Jun & 2018 Aug&\\
		\href{https://github.com/maxlevesque/laboetie}{laboetie} & 2014 Nov & 2018 Aug&\\		
		\href{https://github.com/UCL/LatBo.jl}{LatBo.jl} & 2014 Aug & 2017 Feb&\\
		\href{https://code.google.com/p/lb2d-prime-dev/source}{LB2D-Prime} & 2005 & 2012 Apr&\\
		\href{http://ccs.chem.ucl.ac.uk/sites/ccs.chem.ucl.ac.uk/themes/ccs2/files/lb3d-2012-03-12.tgz}{LB3D} & unclear & 2012 Mar&\\
		\href{https://code.google.com/archive/p/lb3d-prime-dev/source}{LB3D-Prime} & 2005 & 2011 Oct&\\
		\href{https://code.google.com/archive/p/limbes/source}{LIMBES} & 2010 Nov & 2014 Dec&\\
		\href{https://github.com/carlosrosales/mplabs}{MP-LABS} & 2008 Jun & 2014 Oct&\\
		\href{https://sourceforge.net/projects/sunlightlb/files/latest/download}{SunlightLB} & 2005 Sep & 2012 Nov&\\
		\bottomrule
	\end{tabular}
	\caption{Dead Software Packages} \label{deadpackages}
\end{center}
\end{table}

>>>>

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3cm}p{2cm}p{2cm}p{5.5cm} }
			\toprule
			Name & Released & Updated & Relevant Publication\\
			\midrule
			\href{https://www.ccp5.ac.uk/sites/www.ccp5.ac.uk/files/dl_meso/data/dl_meso_2.7.zip}{DL\_MESO (LBE)} & unclear & 2020 Mar&\citep{seaton2013dlmeso}\\
			\href{https://github.com/espressomd/espresso}{ESPResSo} & 2010 Nov & 2020 Jun&\citep{weik2019espresso}\\
			\href{https://github.com/espressopp/espressopp}{ESPResSo++} & 2011 Feb & 2020 Apr&\citep{halverson2013espresso++}\\
			\href{https://github.com/mabau/lbmpy}{lbmpy}& unclear  & 2020 Jun & \citep{bauer2021lbmpy}\\
			\href{https://github.com/Olllom/lettuce}{lettuce} & 2019 May & 2020 Jul&\citep{bedrunka2021lettuce}\\
			\href{https://github.com/ludwig-cf/ludwig}{Ludwig} & 2018 Aug & 2020 Jul&\citep{desplat2001ludwig}\\
			\href{https://github.com/aharwood2/LUMA}{LUMA} & 2016 Nov   & 2020 Feb &\citep{harwood2018luma}\\
			\href{http://hg.savannah.gnu.org/hgweb/mechsys/file/tip/}{MechSys} & 2008 Jun    & 2021 Oct &\citep{galindo2013coupled}\\
			\href{https://osdn.net/projects/apes/scm/hg/musubi/}{Musubi} & 2013 Sep & 2019 Aug &\citep{hasert2014complex}\\
			\href{https://www.openlb.net/download/}{OpenLB} & 2007 Jul & 2019 Oct &\citep{heuveline2010openlb}\\
			\href{https://gitlab.com/unigespc/palabos}{Palabos} & unclear & 2020 Jul &\citep{latt2021palabos}\\
			\href{https://github.com/pylbm/pylbm}{pyLBM} & 2015 Jun&   2020 Jun &\\
			\href{https://github.com/sailfish-team/sailfish}{Sailfish} & 2012 Nov & 2019 Jun & \citep{januszewski2014sailfish}\\
			\href{https://github.com/CFD-GO/TCLB}{TCLB} & 2013 Jun  & 2020 Apr & \citep{rokicki2016adjoint}\\
			\href{https://i10git.cs.fau.de/walberla/walberla}{waLBerla} & 2008 Aug & 2020 Jul & \citep{bauer2021walberla}\\
			\bottomrule
		\end{tabular}
		\caption{Alive Software Packages} \label{alivepackages}
	\end{center}
\end{table}

@@

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3cm}p{2cm}p{2cm}p{5.5cm} }
			\toprule
			Name & Released & Updated & Relevant Publication\\
			\midrule
			\href{https://github.com/UCL/hemelb}{HemeLB} & 2007 Jun & 2018 Aug&\citep{mazzeo2008hemelb}\\
			\href{https://github.com/maxlevesque/laboetie}{laboetie} & 2014 Nov & 2018 Aug&\citep{levesque2013accounting}\\		
			\href{https://github.com/UCL/LatBo.jl}{LatBo.jl} & 2014 Aug & 2017 Feb&\\
			\href{https://code.google.com/p/lb2d-prime-dev/source}{LB2D-Prime} & 2005 & 2012 Apr&\\
			\href{http://ccs.chem.ucl.ac.uk/sites/ccs.chem.ucl.ac.uk/themes/ccs2/files/lb3d-2012-03-12.tgz}{LB3D} & unclear & 2012 Mar&\citep{schmieschek2017lb3d}\\
			\href{https://code.google.com/archive/p/lb3d-prime-dev/source}{LB3D-Prime} & 2005 & 2011 Oct&\\
			\href{https://code.google.com/archive/p/limbes/source}{LIMBES} & 2010 Nov & 2014 Dec&\\
			\href{https://github.com/carlosrosales/mplabs}{MP-LABS} & 2008 Jun & 2014 Oct&\\
			\href{https://sourceforge.net/projects/sunlightlb/files/latest/download}{SunlightLB} & 2005 Sep & 2012 Nov&\\
			\bottomrule
		\end{tabular}
		\caption{Dead Software Packages} \label{deadpackages}
	\end{center}
\end{table}
